%   Filename    : chapter_1.tex 
\chapter{Introduction}
\label{sec:researchdesc}    %labels help you reference sections of your document
\vspace*{-1cm}  % Adjust as needed
\section{Overview}
\label{sec:overview}
The tuna supply chain faces critical issues that affect both the industry and its consumers. Illegal fishing, overfishing, and poor traceability threaten the sustainability and ethical trade. A lack of transparency compromises product quality and misleads consumers. Blockchain technology can address these challenges by tracking the tuna's journey from ocean to plate through a secure, tamper-proof ledger. This system also holds stakeholders to comply to legal standards.

\noindent Although blockchain integration in the tuna sector is underway, gaps remain in its implementation. This study helps to address the industry’s need for transparent and secure tracking of tuna products from ocean to consumer, while assessing the feasibility of implementing blockchain at scale in the seafood sector.


\section{Problem Statement}

Fish is one of the most consumed protein products in the Philippines. Before the COVID-19 pandemic, fish was the most consumed animal protein in the Philippines with annual per capita consumption of 40 kg (Agriculture and Agri-Food Canada, 2022). Among the wide variety of fish, tuna stands out as a particularly significant commodity due to its high demand and economic value. Although the nation is gifted with an abundance of aquatic resources, the methods of dispersal of the product usually leads to inefficiency in terms of sales, pricing, and overall product quality for the consumers. The problem arises with the introduction of a supply chain from several middlemen between the fish farmer or producer and wholesaler in the coastal and aquatic regions towards the consumers with less access to fresh fish. Consequently, both consumers and suppliers struggle to ensure transparent and fair pricing, accurately track tuna products, and maintain consistent quality. These challenges stem from inefficient methods of product dispersal and the presence of multiple intermediaries between fisherfolks in coastal municipalities and consumers. This fragmented supply chain introduces delays, obscures product origin, and opens opportunities for mishandling or mislabeling. To address this, the study focuses on the absence of a reliable, real-time traceability system that allows stakeholders to verify the origin, novelty, handling processes, and adherence to ethical sourcing practices of tuna at every stage. Without such a system, the tuna supply chain and industry lack the transparency and accountability necessary to build consumer trust and improve supply chain efficiency. By introducing a blockchain-driven solution, this study aims to streamline the traceability process and reduce the negative impact of intermediary-heavy distribution.



\section{Research Objectives}
\label{sec:researchobjectives}

\subsection{General Objective}
\label{sec:generalobjective}

The general objective of the study is to design and develop a blockchain-driven application that improves the traceability of the tuna supply chain. Given the timely issues regarding illegal, unreported and unregulated (IUU) fishing and lack of product traceability and transparency, this study addresses these challenges through an application that has the capability to provide an immutable ledger and tamper-proof records. The result of this study serves as a framework for integrating blockchain technology in the fish supply chain, specifically for tuna. This also supports future researchers and developers facing similar challenges in the industry.


\subsection{Specific Objectives}
\label{sec:specificobjectives}

To further specify the research objectives, the study focuses to:

\begin{enumerate}
	
	\item develop a smart contract framework using blockchain technology for data verification and transaction recording, ensuring secure and tamper-proof data for the stakeholders,
	\item design and develop a blockchain-driven application with a user-friendly interface that allows stakeholders to access and input data while enhancing traceability in the tuna supply chain through a tuna asset record for the supply chain participants, and 
	\item deploy the application after completing all necessary preparations for software development and to evaluate its overall results and effectiveness in enhancing the tuna supply chain, as discussed in the fourth and fifth chapters of the study.
\end{enumerate}


\section{Scope and Limitations of the Research}
\label{sec:scopelimitations}

The scope of this study focuses on how blockchain technology can be applied to enhance traceability and transparency within the tuna supply chain. It involves features such as smart contracts for recording the transactions and user interface for stakeholders. The study also focuses exclusively on whole, small-sized caught tuna products in the supply chain, excluding processed forms such as canned or packaged tuna. The research examines the traceability of whole tuna from capture to market sale, specifically centering on a supplier based in Miagao and San Joaquin, Iloilo. 

\noindent This study focuses solely on the supply chain in within the specified municipalities of Iloilo, so findings may not fully represent global practices. As it concentrates on blockchain's role in traceability, other potential functions of the technology fall outside of the scope of this research.


\begin{comment}
	
	%
	% IPR acknowledgement: the sentences inside this comment are from Ethel Ong's slides on Scope and Limitations of the Research
	%
	Generally, one paragraph should be allotted for each of your research objectives.
	
	Each paragraph contains a brief overview of the concept/theory and the purpose of doing the associated objective.
	
	Each paragraph also includes a description of the scope/limitation of your study.
	
	* Please refer to the slides for examples.
	
\end{comment}


\section{Significance of the Research}
\label{sec:significance}

This study serves a significant purpose for several stakeholders in the tuna supply chain. This study aims to solve the problems related to the management of tuna supply chain, particularly with regards to product traceability.
%STAKEHOLDERS
\begin{itemize}
	\item The Stakeholders 
	\begin{itemize}
		\item This study enhances transparency and accountability, allowing stakeholders such as fishers, suppliers, and retailers to access tamper-proof and accurate information, thereby promoting a more ethical and authentic supply chain. By providing a digital record of the product’s history, this study helps ensure compliance with environmental and legal standards. In cases of anomalies such as oil spills, red tide occurrences, and illegal fishing activities, stakeholders can be involved in identifying and addressing these issues, fostering a collaborative approach to sustainability. Similarly, the record of a tuna asset can be utilized for accountability purposes when problems such as damaged products, mislabeling, or contamination arise, allowing stakeholders to trace and resolve them efficiently.
	\end{itemize}
\end{itemize}
% CONSUMERS
\begin{itemize}
	\item The Consumers
	\begin{itemize}
		\item This study helps consumers verify the history of the tuna product from its origin up until its journey to the consumers, therefore increasing trust and transparency. By promoting traceability, it offers a more detailed and verifiable record of the supply chain, enabling consumers to assess sustainability practices and identify stakeholders responsible for any potential issues affecting the tuna product. This, in turn, encourages critical evaluation of the tuna supply chain, driving improvements in accountability, resource management, and ethical sourcing.
	\end{itemize}
\end{itemize}
%FUTURE RESEARCHERS
\begin{itemize}
	\item For Future Researchers
	\begin{itemize}
		\item As blockchain technology continues to grow, this study contributes to the application of blockchain in the supply chain management and the insights regarding its benefits and limitations. This research can be helpful in the growing knowledge on digital solutions for traceability and transparency for future research. 
	\end{itemize}
\end{itemize}
\begin{itemize}
	\item The Policy Makers 
	\begin{itemize}
		\item This study provides policy makers a reliable and data-driven foundation in monitoring and regulating the tuna supply chain. By leveraging tamper-proof and transparent records, policymakers can more effectively enforce compliance with fishing quotas and environmental protections. This research also aids in lessening the illegal, unreported and unregulated (IUU) fishing practices, contributing to the national sustainability goals. 
	\end{itemize}
\end{itemize}

\begin{comment}
	If applicable, describe possible commercialization and/or innovation in your research.
\end{comment}


