%   Filename    : dedication.tex 
\begin{center}
	\textbf{Dedication}
\end{center}

This Special Problem, SeaXChange: A Blockchain-Driven App for Tuna Supply Chain Management, is dedicated to those who were instrumental in its creation and purpose:

To our esteemed adviser and mentor, \textbf{Francis D. Dimzon, Ph.D.}, for his invaluable guidance, expertise, and unwavering support throughout our research journey.

To the members of the \textbf{Miagao community}, particularly the fishermen, suppliers, and retailers from \textbf{Barangay Sapa}, and the consumers from \textbf{Barangay Mat-y}—your daily experiences and challenges in ensuring transparent pricing, product tracking, and maintaining fish product quality served as the foundational motivation for this study. Your participation and insights were crucial.

To \textbf{Engr. Noel Lucero}, whose valuable perspectives during interviews provided essential context for understanding current trends and issues in the tuna supply chain and the fishing industry as a whole.

To our fellow Special Problem classmates and colleagues—for the collaboration, shared challenges, and mutual support that made this academic endeavor more enriching.

And most importantly, to our beloved families—for their constant love, encouragement, understanding, and sacrifices that enabled us to pursue and complete this work.

This Special Problem paper stands as a testament to your support and as a contribution toward addressing the challenges faced within the tuna supply chain.
